Representation Learning for Generalized Planning - SAT Encodings

### 2021-04-23 doc/paper/paper.tex
Adapt PDF encoding to fixed pool of actions

\subsection{Terminology}
A state is called \emph{reachable} if there is a path to it from $s_0$, and
it is called \emph{solvable} if there is a path from it to a goal
state.
A state is \emph{alive} if it is solvable, reachable and not a
goal state~\cite{frances-et-al-ijcai2019}.

We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.

@@

\paragraph{Feature dominance.}
Work In Progress.\footnote{This is implemented, but needs to be adapted to the equivalence classes improvement.}

@@

\subsection{Variables}

\subsubsection{Main Variables}

Let the transitions be defined as $s \rightarrow a \rightarrow s' \rightarrow s"$, where the agent executes a in the state s and goes to some $s'$, and then the nature or the adversary (doing anything) turns $s'$ into $s''$. Therefore the transitions $(s, s')$ is deterministic and the transition $(s, s'')$ is non-deternimistic.

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, $s''$ solvable. Where $V(s'') < V(s)$.

 \item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.

@@

\subsection{Hard Constraints}

\smallpar{C1}
The policy has to be complete with respect to all alive states:
\begin{align}
\bigvee_{s' \text{ s.t. } (s, s') \in T \setminus \badtx} Good(s, s'),&\;\; \text{for $s$ alive.}
\end{align}

\smallpar{C2} $V$ is always descending along Good transitions:
\begin{align}
 Good(s, s') \land V(s', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $d \in [1, D)$.} \\
 V(s', D) \rightarrow \neg Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$.} \tag{\theequation${}^\prime$}
\end{align}

\smallpar{C3 (Optional)} All descending transitions must be considered Good:
\begin{align}
 V(s, d) \land V(s', d') \rightarrow Good(s, s'),&\;\; \text{for $s, s'$ alive, $(s, s') \not\in \badtx$, $1 \leq d' < d \leq D$,} \\
 Good(s, s'),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
\end{align}

@@

\smallpar{C5-6}
Good transitions can be distinguished from bad transitions.
Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
of two different equivalence classes such that $(s, s') \not\in \badtx$
(which implies that $s'$ is solvable). Then,

\begin{align}
 Good(s, s') \rightarrow Good(t, t') \lor
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \not\in \badtx$.} \\
 Good(s, s') \rightarrow
 Dist(s, s', t, t'),&\;\; \text{for $s, t$ alive, $(t, t') \in \badtx$.}
\end{align}

@@

\smallpar{C8 (Optional)}
All selected features need to have some Good transition that takes them to $0$:
\begin{align}
 Selected(f) \rightarrow \bigvee_{(s, s') \in Z(f)} Good(s, s'),&\;\; \text{for $f$ in pool}
\end{align}

\noindent where $Z(f)$ is the set transitions starting in an alive state that change the denotation of $f$ from something
larger than 0 to 0.

\subsection{Soft Constraints}
We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.

\section{Empirical Results}

>>>>

\subsection{Terminology}
A state is called \emph{reachable} if there is a path to it from $s_0$, and
it is called \emph{solvable} if there is a path from it to a goal
state.
A state is \emph{alive} if it is solvable, reachable and not a
goal state~\cite{frances-et-al-ijcai2019}.
We use $T$ to denote the set of all transitions $(s, s')$ in the training sample such that $s$ is alive.

@@

@@

\subsection{Fixed Pool $A$ of actions}

We here assume that all instances $P$ of the generalized problem have the same fixed set of actions $A$.
We denote by $(s, a, s'') \in T$ tuples of state, action, and possible state $s''$ resulting from the adversary
response to the application of $a$ in $s$.

\subsubsection{Variables}

\begin{itemize}
 \item $Good(s, a)$ for $s$ alive, solvable, and $a \in A$.

 \item $Bad(s)$ for $s$ alive.

 %\item $Good(s, s')$ for $s$ alive, $s'$ solvable and $(s, s') \not\in \badtx$.

@@

\subsubsection{Hard Constraints}

\smallpar{C1}
The policy has to be complete with respect to all possible actions applicable in s:
\begin{align}
\bigvee_{a \in A} Good(s, a),&\;\; \text{for $s$ alive.}
\end{align}

\smallpar{C2} $V$ is always descending along Good actions:
\begin{align}
 Good(s, a) \land V(s'', d) \rightarrow \bigvee_{d < k \leq D} V(s, k),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $d \in [1, D)$.} \\
 V(s'', D) \rightarrow \neg Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$.} \tag{\theequation${}^\prime$}
\end{align}

%\smallpar{C3} All descending transitions must be considered Good:
%\begin{align}
% V(s, d) \land V(s'', d') \rightarrow Good(s, a),&\;\; \text{for $s$ alive, $(s, a, s'') \in T$, $1 \leq d' < d \leq D$,} \\
% Good(s, a),&\;\; \text{for $s$ alive, $s'$ goal.} \tag{\theequation${}^\prime$}
%\end{align}

@@

\smallpar{C5-6}
Good pairs $(s, a)$ can be distinguished from bad pairs $(s, a)$.
%Let $(s, s')$ and $(t, t')$ be \emph{representative} transitions
%of two different equivalence classes such that $(s, s') \not\in \badtx$
%(which implies that $s'$ is solvable). Then,
\begin{align}
 Good(s, a) \rightarrow Good(t, a) \lor
 D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \not\in \badtx$.} \\
 Good(s, a) \rightarrow D1(s, t),&\;\; \text{for $s, t$ alive, $(t, a) \in \badtx$.}
\end{align}

@@

\subsubsection{Soft Constraints}
We simply post a constraint $\neg Select(f)$ for each feature $f$ in the pool, with weight equal to its complexity $\mathcal{K}(f)$.
